\bf Model Visualization Techniques for a Social Network Model

### 2018-04-02 paper-child.Rnw
committing for safekeeping

set.seed(12345)
ggplot(data = jTT, aes(from_id = from, to_id = to)) +
  geom_net(aes(shape = as.factor(group)), directed = T, labelon = T,
           labelcolour='grey80',vjust = 0.5, hjust =0.5, arrowgap = .15,
           colour = 'black', size=10, fontsize = 5,
           ecolour = c("grey40", "grey40","red", "grey40")) +
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  ThemeNet +
  theme(legend.position = "none")
@
\caption{\label{fig:jtt}Realization of a jumping transitive triplet, where $i$ is the focal actor, $j$ is the target actor, and $h$ is the intermediary. The group of the actors is represented by the shape of the node.}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
<<dab, echo=FALSE, fig.width=2, fig.height=2, message = FALSE, warning = FALSE, fig.align='center', out.width='.49\\textwidth'>>=
dade <- data.frame(from = c('i', 'i', 'h', 'j'), to = c('h', 'j', 'k', 'k'))
dadn <- data.frame(id = letters[8:11], group = c(1,1,1,1))

@@

set.seed(12345)
ggplot(data = dad, aes(from_id = from, to_id = to)) +
  geom_net(aes(shape = as.factor(group)), directed = T, labelon = T, labelcolour='grey80',vjust = 0.5, hjust =0.5, arrowgap = .15, colour = 'black', size=10, fontsize = 5) +
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  ThemeNet +
  theme(legend.position = "none")
@
\caption{\label{fig:dad}Doubly achieved distance between actors $i$ and $k$.}
\end{subfigure}
\caption{The additional network effects included in our models fit to the friends data. On the left, a jumping transitive triplet (JTT). On the right, a doubly achieved distance between $i$ and $k$.}
\end{figure}

@@

combinedavgs %>% filter(cat == "Model1") %>% mutate(logweight = log(weight)) -> t1
colors <- tweenr::tween_color(data = c("#969696", "#d73027"), n = 26, ease = 'linear')
t1 %>% arrange(logweight) -> t1
t1$color <- NA
t1$color[1:26] <- colors[[1]]

@@

<<averagenet, results='hide', out.width='\\textwidth',fig.cap='The node-link diagrams from the three "average" networks that we calculated are in the top row, and the true wave 1 and wave 2 data are shown in the bottom row above. There is some difference between the three models, but overall, these three models cannot capture the structure in the true second wave of data.', fig.height=5>>=
#friend.data.w1 <- as.matrix(read.table("s50_data/s50-network1.dat"))
#friend.data.w2 <- as.matrix(read.table("s50_data/s50-network2.dat"))
#friend.data.w3 <- as.matrix(read.table("s50_data/s50-network3.dat"))
#drink <- as.matrix(read.table("s50_data/s50-alcohol.dat"))
friendshipData <- array(c(fd2.w1, fd2.w2, fd2.w3), dim = c(16, 16, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
M2eff <- includeEffects(M1eff, jumpXTransTrip, interaction1 = "alcohol")
M3eff <- includeEffects(M1eff, nbrDist2twice)
data(M1ests_bigfriends)
M1parms <- (means %>% filter(Model == "M1"))$means
M2parms <- (means %>% filter(Model == "M2"))$means
M3parms <- (means %>% filter(Model == "M3"))$means
# M1sims1000 <- saom_simulate(dat = mydata,
#                             struct = M1eff,
#                        parms = as.numeric(M1parms),
#                        N = 1000)
# M2sims1000 <- saom_simulate(dat = mydata,
#                             struct = M2eff,
#                        parms = as.numeric(M2parms),
#                        N = 1000)
# M3sims1000 <- saom_simulate(dat = mydata,
#                             struct = M3eff,
#                        parms = as.numeric(M3parms),
#                        N = 1000)
# M1simsdf <- sims_to_df(M1sims1000)
# M2simsdf <- sims_to_df(M2sims1000)
# M3simsdf <- sims_to_df(M3sims1000)
M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>%
  summarise(count = n()) %>%
  mutate(weight = ifelse(from == to, 0, count))
M1avgW2 <- M1simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>%
  summarise(count = n()) %>%
  mutate(weight = ifelse(from == to, 0, count))
M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M2avg <- M2simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>%
  summarise(count = n()) %>%
  mutate(weight = ifelse(from == to, 0, count))
M2avgW2 <- M2simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>%
  summarise(count = n()) %>%
  mutate(weight = ifelse(from == to, 0, count))
M2avg2 <- M2simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M3avg <- M3simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>%
  summarise(count = n()) %>%
  mutate(weight = ifelse(from == to, 0, count))
M3avgW2 <- M3simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>%
  summarise(count = n()) %>%
  mutate(weight = ifelse(from == to, 0, count))
M3avg2 <- M3simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))

>>>>

set.seed(12345)
ggplot(data = jTT, aes(from_id = from, to_id = to)) +
  geom_net(aes(shape = as.factor(group)), directed = T, labelon = T,
           labelcolour='grey80',vjust = 0.5, hjust =0.5, arrowgap = .15,
           colour = 'black', size=10, fontsize = 5,
           ecolour = c("grey40", "grey40","red", "grey40")) +
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  ThemeNet +
  theme(legend.position = "none")
@
\caption{\label{fig:jtt}Realization of a jumping transitive triplet, where $i$ is the focal actor, $j$ is the target actor, and $h$ is the intermediary. The group of the actors is represented by the shape of the node.}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
<<dab, echo=FALSE, fig.width=2, fig.height=2, message = FALSE, warning = FALSE, fig.align='center', out.width='.49\\textwidth'>>=
dade <- data.frame(from = c('i', 'i', 'h', 'j', 'i'), to = c('h', 'j', 'k', 'k','k'))
dadn <- data.frame(id = letters[8:11], group = c(1,1,1,1))

@@

set.seed(12345)
ggplot(data = dad, aes(from_id = from, to_id = to)) +
  geom_net(directed = T, labelon = T,
           ecolour = c("black", "black", "black","red", "black" ,"black" ),
           labelcolour='grey80',vjust = 0.5, hjust =0.5, arrowgap = .15, size=10, fontsize = 5) +
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  ThemeNet +
  theme(legend.position = "none")
@
\caption{\label{fig:dad}Doubly achieved distance between actors $i$ and $k$.}
\end{subfigure}
\caption{The additional network effects included in our models fit to the friends data. On the left, a jumping transitive triplet (JTT). On the right, a doubly achieved distance between $i$ and $k$.}
\end{figure}

@@

combinedavgs %>% filter(cat == "Model1") %>% mutate(logweight = log(weight)) -> t1
colors <- tweenr::tween_color(data = c("#969696", "#d73027"), n = table(t1$cat) %>% as.numeric, ease = 'linear')
t1 %>% arrange(logweight) -> t1
t1$color <- NA
t1$color <- colors[[1]]

@@

<<averagenet, results='hide', out.width='\\textwidth',fig.cap='The node-link diagrams from the three "average" networks that we calculated are in the top row, and the true wave 1 and wave 2 data are shown in the bottom row above. There is some difference between the three models, but overall, these three models cannot capture the structure in the true second wave of data.', fig.height=5>>=
#friend.data.w1 <- as.matrix(read.table("s50_data/s50-network1.dat"))
#friend.data.w2 <- as.matrix(read.table("s50_data/s50-network2.dat"))
#friend.data.w3 <- as.matrix(read.table("s50_data/s50-network3.dat"))
#drink <- as.matrix(read.table("s50_data/s50-alcohol.dat"))
# friendshipData <- array(c(fd2.w1, fd2.w2, fd2.w3), dim = c(16, 16, 3))
# friendship <- sienaDependent(friendshipData)
# alcohol <- varCovar(drink[20:35,])
# mydata <- sienaDataCreate(friendship, alcohol)
# M1eff <- getEffects(mydata)
# M2eff <- includeEffects(M1eff, jumpXTransTrip, interaction1 = "alcohol")
# M3eff <- includeEffects(M1eff, nbrDist2twice)
# data(M1ests_bigfriends)
# M1parms <- (means %>% filter(Model == "M1"))$means
# M2parms <- (means %>% filter(Model == "M2"))$means
# M3parms <- (means %>% filter(Model == "M3"))$means
# M1sims1000 <- saom_simulate(dat = mydata,
#                             struct = M1eff,
#                        parms = as.numeric(M1parms),
#                        N = 1000)
# M2sims1000 <- saom_simulate(dat = mydata,
#                             struct = M2eff,
#                        parms = as.numeric(M2parms),
#                        N = 1000)
# M3sims1000 <- saom_simulate(dat = mydata,
#                             struct = M3eff,
#                        parms = as.numeric(M3parms),
#                        N = 1000)
# M1simsdf <- sims_to_df(M1sims1000)
# M2simsdf <- sims_to_df(M2sims1000)
# M3simsdf <- sims_to_df(M3sims1000)
# M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
#   group_by(from, to) %>%
#   summarise(count = n()) %>%
#   mutate(weight = ifelse(from == to, 0, count))
# M1avgW2 <- M1simsdf %>% filter(!is.na(to) & wave == 2) %>%
#   group_by(from, to) %>%
#   summarise(count = n()) %>%
#   mutate(weight = ifelse(from == to, 0, count))
# M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
#  group_by(from, to, wave) %>%
#  summarise(count = n()) %>%
#  mutate(weight = ifelse(from == to, 0, count))
# M2avg <- M2simsdf %>% filter(!is.na(to) & wave == 1) %>%
#   group_by(from, to) %>%
#   summarise(count = n()) %>%
#   mutate(weight = ifelse(from == to, 0, count))
# M2avgW2 <- M2simsdf %>% filter(!is.na(to) & wave == 2) %>%
#   group_by(from, to) %>%
#   summarise(count = n()) %>%
#   mutate(weight = ifelse(from == to, 0, count))
# M2avg2 <- M2simsdf %>% filter(!is.na(to)) %>%
#  group_by(from, to, wave) %>%
#  summarise(count = n()) %>%
#  mutate(weight = ifelse(from == to, 0, count))
# M3avg <- M3simsdf %>% filter(!is.na(to) & wave == 1) %>%
#   group_by(from, to) %>%
#   summarise(count = n()) %>%
#   mutate(weight = ifelse(from == to, 0, count))
# M3avgW2 <- M3simsdf %>% filter(!is.na(to) & wave == 2) %>%
#   group_by(from, to) %>%
#   summarise(count = n()) %>%
#   mutate(weight = ifelse(from == to, 0, count))
# M3avg2 <- M3simsdf %>% filter(!is.na(to)) %>%
#  group_by(from, to, wave) %>%
#  summarise(count = n()) %>%
#  mutate(weight = ifelse(from == to, 0, count))
